%%%%%%%%%%%%%%%%%%%%%%%%% Tools %%%%%%%%%%%%%%%%%%%%%%%

\section{Tools}
\label{sec:tools}
In this section we will describe briefly the main tools employed for the
achievement of this project. 
There have been a personal interest in the use of free or open-source software
due to all the advantages that it offers to us. Therefore, all the tools we 
have employed (except Jude, which was used under a freeware license) have a
license of these characteristics.

The list below, summarizes the most important tools employed for this project:

\begin{itemize}
  %\item Ubuntu GNU/Linux, versions 8.04 and 8.10. Free software operating
  %system.
  \item Eclipse 3.4.1 as IDE, including the following plugins (all of them free
  or open source software):
  		\begin{itemize}
            \item Knopflerfish OSGi IDE, version 1.0.16. Plugin to help in OSGi
            bundles development (see Section
            \ref{subsubsec:tech-osgi-knopflerfish}).
            \item Subclipse, version 1.4.8. Provides support for Subversion.
            \item Visual Swing, version 0.9. Provides visual GUI design tools.
            \item Textlipse, version 1.3.0. Provides \LaTeX{} support.
          \end{itemize}
   \item Knopflerfish, version 2.3. Open source OSGi service platform.
   \item MySQL, version 5.1. Open source RDBMS (see Section
   \ref{subsec:tech-mysql}).
   \item PHPMyAdmin, version 3.2. Open source tool to handle MySQL
   administration through a web interface.
   \item Apache, version 2.2. Free software HTTP server.
   \item Dia, version 0.96. Free software program to draw diagrams.
   \item Jude Community, version 5.4.1. Freeware program for UML modeling.
   \item VirtualBox, version 3.0.2. Open source virtualizer for x86 hardware.
   \item GIMP, version 2.6. Free software for image manipulation.
          
\end{itemize}
