\chapter{Objectives}
\label{chap:objectives}

In this section we will state briefly the main goals of the project. The way in
which these objectives were achieved will be discussed in Chapter
\ref{chap:description}.
\par

The main objectives of this project are:

\begin{itemize}
  \item Create a main repository for applications, where the users can browse,
  share and retrieve them. This should be accomplished taking into account:
  \begin{itemize}
    \item The sharing process has to be flexible enough to allow the user
    choosing in which communities the application is going to be shared, and
    which rules are going to be shared.
    \item The retrieving process has to be flexible enough to allow the user a
    customization of the retrieved application. 
    \item The changes needed to adapt the application have to be as transparent
    to the user as possible.
    \item It is necessary to implement a mechanism which allows the user to
    search for applications:
      \begin{itemize}
        \item By different criteria: tags, description, type, etc.
        \item Using a system recommendation process, where the user just has to
        select an application and some similar applications will be suggested.
      \end{itemize}
  \end{itemize}
  
  \item Create a system which allows the users to tag the applications. This
  should be accomplished taking into account the need of different scopes for
  the tags:
  \begin{itemize}
    \item Private tags, which are only for personal purposes and should not be
    stored in the Backend.
    \item Community tags, which are only visible for members of that community.
    \item Public tags, which are visible for all the members.
  \end{itemize}
  
  
  \item Create a GUI which allows the user to carry out the operations defined
  previously. This should be performed taking into account:
  \begin{itemize}
    \item The GUI has to be connected with the rest of systems in a loose
    coupling way.
    \item It has to be intuitive.
    \item It has to be extensible, so other systems can be connected to it in
    the future.
  \end{itemize}
\end{itemize}