
\section{Conclusions \& future work}

\begin{frame}

	\frametitle{Conclusions \& future work} 
	\begin{itemize}
	  \item Achieved goals:
	 	\begin{itemize}
	  		\item Successful development and integration of a set of
				bundles to manage awareness applications into ASTRA, including 
				functionalities for sharing, tagging, locating, appropriating and 
				adapting the applications.
			\item New GUI, which demonstrates the flexibility of ASTRA SOA.
			\item Stressing its extensibility, so new functionalities can be easily
			added.
		\end{itemize}	 
	\end{itemize}

	\begin{itemize}
	  \item Future work:
	 	\begin{itemize}
	  		\item Adjust searching by similarity parameters, once we have real users
	  	 	data.
			\item Use of ontologies for helping in the application adaptation process,
			once \texttt{OntologyManager} services are implemented
			(\texttt{ApplicationManager} is already prepared).
			\item Extend the GUI: new browsing capabilities, join communities, rules
			edition, etc.
		\end{itemize}	 
	\end{itemize}


\end{frame}

\begin{frame}

	\begin{itemize}
	  \item Contribution \& Personal evaluation:
	 	\begin{itemize}
	  		\item I started my contribution to ASTRA as part of my summer job for NTNU
	  		during the summer of 2008: iterations 1 \& 2.
			\item I resumed my collaboration with ASTRA project in February 2009,
			working from Madrid: iterations 3 \& 4.
			\item I came back to Norway to work in ASTRA during one month and a half
			during the summer: very useful to elicit and implement last requirements.
			\item It has been a very enriching experience: opportunity of working in a
			real researching project collaborating with teams from several
			countries, in technological terms, etc.
		\end{itemize}	 
	\end{itemize}

\end{frame}
