\section{Testing}

\begin{frame}

	\frametitle{Testing} 
	
	Testing in different levels:
	
	\begin{itemize}

        \item Functionalities verification (low and high level): visibility,
        network is down, extreme cases, etc.
        \item Different OS compatibility: GNU/Linux, Windows XP, etc.
        \item Preliminary users evaluation (iterations 1 \& 2):
        \begin{itemize}
          \item Performed at NTNU (Trondheim) in December 2008.
          \item Users were very positive about the idea of sharing/getting
          applications, about the notion of community, etc.
          \item Very useful for adding new functionalities in iterations 3 \& 4:
          searching by criteria, searching by similarity, application
          adaptation, etc.
        \end{itemize}
        \item New user evaluation (including iterations 3 \& 4) is scheduled in
        October 2009.

	\end{itemize}

\end{frame}

\subsection{Search engine testing (similarity)}

\begin{frame}

	\frametitle{Ex.: search engine testing (similarity)} 

	\begin{itemize}
	    \item Set of 25 applications, with a description and a set of 4 tags
	    for each of them.
	    \item Divided into 5 groups: ``Sport'', ``Social'', ``Feelings'',
	    ``Cultural'' and ``Location''.
	    \item We assumed an application can only belong to one of this groups
	    to make the measuring process simpler, but this introduces an error, since the way an application is categorized is
		subjective and not exclusive. 
		\item We calculate precision and recall.
    \end{itemize}
    
    \[precision = (Relevant\phantom{i}docs/Total\phantom{i}retrieved\phantom{i}docs)*100\]
	\[recall = (Relevant\phantom{i}docs/Existing\phantom{i}relevant\phantom{i}docs)*100\]
\end{frame}


\begin{frame}

\begin{columns}

	\begin{column}{6cm}
	
	\begin{itemize}
		\item Expected values: \\ p = 40\%, r = 80\%.
		\item Results were quite positive: \\ p = 52\%, r = 96\% \ldots but this is
		based on artificial data.
		\item Useful to check design decisions point to the right way and to set
		guidelines for October's evaluation.
	\end{itemize}
		
	
	\end{column}
	
		\begin{column}{6cm}
	    
\begin{table}[h!]
	\tiny
    \begin{center}
		\begin{tabular}{||c|c|c|c|c|c||}

		\hline \hline
			Group & RD & RDR & ERD & Precision & Recall \\
		\hline \hline
			Sport & 9 & 5 & 5 & 55.56\% & 100\%\\
			\hline
			Social & 10 & 5 & 5 & 50\% & 100\%\\
			\hline
			Feelings & 10 & 5 & 5 & 50\% & 100\%\\
			\hline
			Cultural & 7 & 4 & 5 & 57.14\% & 80\%\\
			\hline
			Location & 10 & 5 & 5 & 50\% & 100\%\\
			\hline
			\hline
			Average & 9.2 & 5 & 5 & 52.54\% & 96\%\\

		\hline \hline

		\end{tabular}
		\caption{\label{table:testing-summary} Summary of the results for search by
		similarity evaluation}
	\end{center}
\end{table}
	    
	    \end{column}
	
\end{columns}

\end{frame}
